Topological Analysis of Bitcoin's Lightning Network

### 2019-01-12 article/main.tex
Fitting gamma ready, Percolation started

\title{Topological Analysis of Bitcoin's Lightning Network }
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show how robust it is against both random failures and targeted attacks. These findings suggest that how LN's topology could be ameliorated in order to achieve its true potential.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

However LN also exhibits somewhat scale-free properties as the s-metric suggests. S-metric was first introduced by Lun Li et al. in \cite{li2005towards} and defined as $s(G)=\sum_{(u,v)\in E}deg(u)deg(v)$. The closer to $1$  s-metric of $G$ is, the more scale-free the network. Diameter and radius of LN suggests that LN is a small world. Somewhat scale-freeness is also exhibited in the degree distribution of LN. Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.

@@

@@

Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes. This would envolve that even the removal of major hubs would leave the connectedness of the major component intact.
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
\section{Acknowledgements}

>>>>

\title{Topological Analysis of Bitcoin's Lightning Network }
\author[1]{István András Seres}
\author[1]{László Gulyás}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show how robust it is against both random failures and targeted attacks. These findings suggest that how LN's topology could be ameliorated in order to achieve its true potential.
\section{Lightning Network's Topology}
\begin{wrapfigure}[22]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

@@

\subsection{Scale-freeness of LN}

LN might exhibit scale-free properties as the s-metric suggests. S-metric was first introduced by Lun Li et al. in \cite{li2005towards} and defined as $s(G)=\sum_{(u,v)\in E}deg(u)deg(v)$. The closer to $1$  s-metric of $G$ is, the more scale-free the network. Diameter and radius of LN suggests that LN is a small world. Somewhat scale-freeness is also exhibited in the degree distribution of LN. Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.

The scale-freeness of LN is further justified also by applying the method introduced in \cite{clauset2009power}. The maximum-likelihood fitting asserted that the best fit for the empirical degree distribution is a power law function with exponent $\gamma=-2.1387$. The goodness-of-fit of the scale-free model was ascertained by the Kolmogorov-Smirnov statistic. We found that the $p$-value of the scale-free hypothesis is $p=0.8172$, which is accurate within $0.01$. Therefore the scale-free hypothesis is plausible for the empirical degree distribution of LN.

@@

Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes. This would envolve that even the removal of major hubs would leave the connectedness of the major component intact.
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
In summary, a better understanding of the network topology is essential
to improve the robustness of complex systems. We can enhance robustness
by either designing network topologies that are simultaneously
robust to both random failures and attacks, or by interventions that limit
the spread of cascading failures.
resilience depends on topology
Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
\section{Acknowledgements}
We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.
